Bound within Boundaries: How Well Do Protected Areas Match Movement Corridors of Their Most Mobile Protected Species?

### 2021-02-17 Chapter_0/04_Manuscript/Manuscript.tex
Various updates

\textbf{Keywords:} dispersal, habitat selection, integrated step selection
function, Kavango-Zambezi Transfrontier Conservation Area, landscape
connectivity, least-cost corridors, Lycaon pictus, permeability surface,
protected areas, wildlife management

@@

Because we were interested in dispersal behavior only, we discarded any GPS data
collected while individuals were still with their natal packs and after
settlement in a new territory \citep{Cozzi.2020}. We identified the exact time
of emigration and settlement based on direct field observations and through
visual inspection of the net squared displacement (NSD) metric. NSD quantifies
the squared Euclidean distance of a relocation to a reference point
\citep{Borger.2012}, which in our case was the center of the dispersing
coalition's natal home range. Thus, dispersal was deemed to have started when a
coalition had left its natal home range and continued until the NSD metric
remained stationary, indicating that the coalition had successfully settled
(Figure S1). In our analysis, we did not differentiate between male and female
dispersing coalitions, for previous research found little differences between
sexes during dispersal \citep{Woodroffe.2019, Cozzi.2020}.

@@

\section{Data Availability}
GPS movement data of dispersing coalitions will be made available on dryad at
the time of publication. R-code showcasing the main steps for sections 2.5 to
2.6 can be downloaded from GitHub
(\url{https://github.com/DavidDHofmann/LeastCostAnalysis}).

>>>>

\textbf{Keywords:} dispersal, habitat selection, integrated step selection
function, Kavango-Zambezi Transfrontier Conservation Area, landscape
connectivity, African wild dog, movement

@@

Because we were interested in dispersal behavior only, we discarded any GPS data
collected while individuals were still with their natal packs and after
settlement in a new territory \citep{Cozzi.2020}. We identified the exact time
of emigration and settlement based on direct field observations and through
visual inspection of the net squared displacement (NSD) metric. NSD quantifies
the squared Euclidean distance of a relocation to a reference point
\citep{Borger.2012}, which in our case was the center of the dispersing
coalition's natal home range. Thus, dispersal was deemed to have started when a
coalition had left its natal home range and continued until the NSD metric
remained stationary, indicating that the coalition had successfully settled
(Figure S1 in Supporting Information). In our analysis, we did not differentiate
between male and female dispersing coalitions, for previous research found
little differences between sexes during dispersal \citep{Woodroffe.2019,
Cozzi.2020}.

@@

\section{Data Availability}
GPS movement data of dispersing coalitions is available in the Dryad Digital
Repository doi:10.5061/dryad.dncjsxkzn \citep{Hofmann.2021}. R-code showcasing
the main steps for sections 2.5 to 2.6 can be obtained through GitHub
(\url{https://github.com/DavidDHofmann/LeastCostAnalysis}).
